Two Mode Networks and Relational Similarity

### 2024-07-13 main.tex
Updates from Overleaf

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr-plot-reord.png}
            \caption{Bonacich Similarity plot (Persons).}
            \label{fig:p-bon-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-sr-plot-eigen.png}
            \caption{Bonacich Similarity plot (Groups).}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-sr-plot-eigen.png}
            \caption{Bonacich correspondence plot.}
            \label{fig:bon-corr}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr.png}
            \caption{Bonacich Similarity plot (Groups).}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-sr-plot-eigen.png}
            \caption{SimRank correspondence plot.}
            \label{fig:sr-corr}
    \end{subfigure}
    \caption{Simrank versus CA comparison. Panel (a) shows the affiliation matrix re-ordered according to the first eigenvector of the SVD of the SimRank similarity matrix. Panels (b) and (d) show the corresponding eigenvector and eigenvalue---panels (c) and (e)---plots for persons and groups, respectively, of the SimRank similarity matrix. Panel (f) shows the correspondence plot based on the eigenvector decomposition of the SimRank similarity matrix. Panels (g) and (h) show the Pearson correlation between the scores corresponding to the first eigenvector of the SimRank similarity matrix (on the y-axis) and the scores corresponding to the first CA dimension (on the x-axis).}
    \label{fig:simrank}
\end{figure}

>>>>

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-ref-corr.png}
            \caption{CA/Reflection Correlation (Persons).}
            \label{fig:p-ca-ref}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-ref-corr.png}
            \caption{CA/Reflection Correlation (Groups)}
            \label{fig:g-ca-ref}
    \end{subfigure}
    \caption{Scatter plot of the scores computed by the method of reflections ($q = 26$) on the y-axis and the first dimension of the Correspondence Analysis of the two-mode affiliation matrix on the x-axis, for both persons (a) and groups (b). }
    \label{fig:ca-ref-corr}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr-plot-reord.png}
            \caption{Re-ordered Affiliation Matrix (SimRank).}
            \label{fig:p-bon-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-sr-plot-eigen.png}
            \caption{SimRank Eigenvector Plot (Persons).}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-sr-plot-eigen.png}
            \caption{SimRank Eigenvector Plot (Groups).}
            \label{fig:bon-corr}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr-corr-plot.png}
            \caption{SimRank Correspondence Plot}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr-corr-scatter.png}
            \caption{SimRank/CA Correlation.}
            \label{fig:sr-corr}
    \end{subfigure}
    \caption{Simrank versus CA comparison. Panel (a) shows the affiliation matrix re-ordered according to the first eigenvector of the SVD of the SimRank similarity matrix. Panels (b) and (c) show the corresponding eigenvector and eigenvalue plots for persons and groups, respectively, of the SimRank similarity matrix. Panel (d) shows the correspondence plot based on the eigenvector decomposition of the first two non-trivial eigenvectors of the SimRank similarity matrix. Panel (e) shows the Pearson correlation between the scores corresponding to the first eigenvector of the SimRank similarity matrix (on the y-axis) and the scores corresponding to the first CA dimension (on the x-axis) for persons (top) and groups (bottom).}
    \label{fig:simrank}
\end{figure}
